Millions of Type Errors

### 2023-09-11 programming23/paper.tex
Updated Roblox stats

{Roblox} is a platform for {shared virtual experiences},
with 56~million Daily Active Users, and 49~billion hours of engagement in
2022~\cite{roblox-quarterly-results}.
There are \textbf{XX}~million creators using {Roblox Studio},
and \textbf{YY}~million creations.

>>>>

{Roblox} is a platform for {shared virtual experiences}, with
65~million Daily Active Users, and 14~billion hours of engagement in
April--June 2023; there are 3~million creators using {Roblox Studio},
creating 5~million experiences~\cite{corp.roblox.com}.
